Cybersecurity Is Too Important\\To Be Left To The Specialists

### 2019-06-15 FIE2019-final-TPJHD.tex
Consistent (and shorter) bibliography

In this paper, we frame a key social, cultural and economic global challenge of cybersecurity in computing and engineering education by analysing the UK's national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities (and into industry and professional practice). Through this analysis of UK educational policy and practice, we make a number of recommendations for future cybersecurity educational initiatives and interventions, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

@@

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]The BCS, The Chartered Institute for IT (BCS) has had a requirement to include information security in the curriculum since 2010, and has expected coverage of an agreed cybersecurity syllabus since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle). More precisely since 2010, accredited degrees have been expected to demonstrate coverage of ``2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information  systems'' \cite[p.~30]{BCS2018a} since 2010 with an enhanced cybersecurity related definition of what this entails since 2015 \cite[p.~17--18]{BCS2018a}.
%BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019): more precisely \cite[Table 3]{Oudshoornetal2018a} ``The computing topics must include: \dots{} Principles and practices for secure computing \dots. This should mean that  all accredited universities should be compliant by 2025 (because of the six-year cycle).
%\cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}
\section{Policy Context}

>>>>

In this paper, we frame a key social, cultural and economic global challenge of cybersecurity in computing and engineering education by dThrough this analysis of UK educational policy and practice, we make a number of recommendations for future cybersecurity educational initiatives and interventions, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

@@

It is at least plausible to attribute this difference to differences in the accreditation regimes.
\begin{description}
\item[UK]The BCS, The Chartered Institute for IT (BCS) has had a requirement to include information security in the curriculum since 2010, and has expected coverage of an agreed cybersecurity syllabus since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle). More precisely since 2010, accredited degrees have been expected to demonstrate coverage of ``2.1.9 Knowledge and understanding of information security issues in relation to the design, development and the use of information  systems'' \cite[p.~30]{BCS2018a} %since 2010 redundant
	with an enhanced cybersecurity related definition of what this entails since 2015 \cite[p.~17--18]{BCS2018a}.
%BCS has had cybersecurity in the curriculum since 2013, and required cybersecurity in accreditation since 2015 (Table \ref{table:1}), with the result that all accredited universities should be compliant by 2020 (because of the five-year cycle).
\item[US]ACM has equally had cybersecurity (``Information Assurance and Security'' --- IAS) in the curriculum since 2013 \cite{ACM2013a}, but it is not the accrediting body. ABET is, and is requiring IAS with effect from the 2019-20 cycle (self study reports due 1 July 2019): more precisely \cite[Table 3]{Oudshoornetal2018a} ``The computing topics must include: \dots{} Principles and practices for secure computing \dots.'' This should mean that  all accredited universities should be compliant by 2025 (because of the six-year cycle).
%\cite[chapter 7]{Davenportminor2019a}.  % need a better reference
\end{description}
\section{Policy Context}
